### 2016-02-15 paper/5-related-work.tex
Made "distribution" more clear in related work; references look more balanced now too

In terms of code design and philosophy, dxex is most related to PythonPDEVS~\cite{PythonPDEVS}.
Performance of PythonPDEVS was still decent, through the use of simulation and activity hints from the modeler.
This allowed the kernel to optimize its internal data structures and algorithms for the specific model being executed.
All changes were completely transparent to the model, and were completely optional.
In this spirit, we offer users the possibility to choose between different synchronization protocols.
This allows users to choose the most appropriate synchronization protocol, depending on the model.
Contrary to PythonPDEVS, however, dxex doesn't support distribution, model migrations~\cite{PythonPDEVS2}, or activity hints~\cite{PythonPDEVS_ACTIMS}.

>>>>

In terms of code design and philosophy, dxex is most related to PythonPDEVS~\cite{PythonPDEVS}.
Performance of PythonPDEVS was still decent, through the use of simulation and activity hints from the modeler.
This allowed the kernel to optimize its internal data structures and algorithms for the specific model being executed.
All changes were completely transparent to the model, and were completely optional.
In this spirit, we offer users the possibility to choose between different synchronization protocols.
This allows users to choose the most appropriate synchronization protocol, depending on the model.
Contrary to PythonPDEVS, however, dxex doesn't support distributed simulation, model migrations~\cite{PythonPDEVS2}, or activity hints~\cite{PythonPDEVS_ACTIMS}.
